---
title: Asynchronous Processing of LEGO Model Prediction
format:
  html:
   code-line-numbers: false
   execute:
     echo: true
     eval: false
---

## Requirements

The current version of our Shiny application contains a module for generating predictions of the number of LEGO parts in a set using the number of unique colors and number of unique part categories. The API is executed and processed using the [`{httr2}`](https://httr2.r-lib.org/) package. Here is the function wrapping the API execution:

```{r}
#' @importFrom httr2 request req_body_json req_perform resp_body_json
run_prediction <- function(df, endpoint_url, back_transform = TRUE, round_result = TRUE) {
  # create request object
  req <- request(endpoint_url)

  # perform request
  resp <- req |>
    req_body_json(df) |>
    req_perform()

  # extract predictions from response
  pred_values <- resp_body_json(resp)$.pred |> unlist()

  # back-transform log10 value of predicted number of parts if requested
  if (back_transform) {
    pred_values <- 10 ^ pred_values
  }

  # round result up to nearest integer if requested
  if (round_result) pred_values <- ceiling(pred_values)

  # append predictions to supplied data frame
  dplyr::mutate(df, predicted_num_parts = pred_values)
}
```

Unfortunately, the prediction API call takes a bit of time to execute due to some **extremely sophisticated processing** 😅. As a result, any interactions within the application will not be processed until the prediction call completes. Our goal is to convert the prediction processing from *synchronous* to *asynchronous* using `{crew}`

## Plan

1. Establish reactive values for tracking the status of the prediction calls
1. Create a new controller to launch new R processes when new prediction tasks are launched
1. Modify the existing `observeEvent` to push the prediction task to the controller, ensuring the key objects and required packages are passed on to the controller.
1. Create a poll that's invalidated every 100 milliseconds to query the status of the submitted tasks in the controller and update the prediction result reactive value when complete.

## Solution 

First we create the following `reactiveVal` objects to keep track of the prediction state:

```{r}
pred_status <- reactiveVal("No prediction submitted yet.")
pred_poll <- reactiveVal(FALSE)
```

Next we set up a new controller:

```{r}
# establish async processing with crew
controller <- crew_controller_local(workers = 4, seconds_idle = 10)
controller$start()

# make sure to terminate the controller on stop #NEW
onStop(function() controller$terminate())
```

Inside the `observeEvent` for the user clicking the prediction button, we update the logic to push the prediction task to the controller:

```{r}
controller$push(
  command = run_prediction(df),
  data = list(
    run_prediction = run_prediction,
    df = pred_data_rv$data
  ),
  packages = c("httr2", "dplyr")
)

pred_poll(TRUE)
```

Lastly, we create a new `observe` block that periodically checks whether the running `{crew}` tasks have completed, ensuring that this is only executed when a prediction has been launched:

```{r}
observe({
  req(pred_poll())

  invalidateLater(millis = 100)
  result <- controller$pop()$result

  if (!is.null(result)) {
    pred_data_rv$data <- result[[1]]
    print(controller$summary()) 
  }

  if (isFALSE(controller$nonempty())) {
    pred_status("Prediction Complete")
    pred_poll(controller$nonempty())
    removeNotification(id = "pred_message")
  }
})
```

